Solving Collective Spin Hamiltonians with Decoherence

### 2018-10-02 soc_squeezing/cumulant_expansions.tex
more work on the product of two operators

@@

@@

  \bigotimes_{\mu,\nu,a} \sigma_{\rho^{\mu\nu}_a}.

@@

Letting $\tilde\rho^{\mu\nu}_\kappa$ denote the number of elements in
$\v\rho^{\mu\nu} \equiv
\p{\rho^{\mu\nu}_1,\rho^{\mu\nu}_2,\cdots,\rho^{\mu\nu}_{r_{\mu\nu}}}$

@@

$\tilde{\v\rho_1}=\tilde{\v\rho_2}$.  We therefore collect such terms
together to write

@@

  \f{r_{\mu\nu}!}{\prod_\kappa\tilde\rho^{\mu\nu}_\kappa!}

@@

counts the degeneracy of terms in \eqref{eq:Q_K_rho}, i.e.~the number
of $\v\rho$ which are consistent with $\tilde{\v\rho}$.

>>>>

  \label{eq:rest_r}

@@

  \label{eq:Q_K_eta}

@@

  \bigotimes_{\mu,\nu,a} \sigma_{\rho^{\mu\nu}_a},

@@

where implicitly $\sum_a\rho^{\mu\nu}_a=r_{\mu\nu}$, as
$\p{\mu,\nu,a}$ essentially index a factor in \eqref{eq:Q_K_eta}, and
$\rho^{\mu\nu}_a$ indexes one of the terms in that factor.  Letting
$\tilde\rho^{\mu\nu}_\kappa$ denote the number of elements in
$\p{\rho^{\mu\nu}_1,\rho^{\mu\nu}_2,\cdots,\rho^{\mu\nu}_{r_{\mu\nu}}}$

@@

$\tilde{\v\rho_1}=\tilde{\v\rho_2}$.  The degeneracy of terms in
\eqref{eq:Q_K_rho}, i.e.~the number of $\v\rho$ which are consistent
with $\tilde{\v\rho}$, is

@@

  \f{r_{\mu\nu}!}{\prod_\kappa\tilde\rho^{\mu\nu}_\kappa!}.

@@

Defining additionally
we can collect like factors and group together equivalent terms in
\eqref{eq:Q_K_rho} to write
  \sigma_\kappa^{\otimes\sum_{\mu,\nu}\tilde\rho^{\mu\nu}_\kappa}
  = \sum_{\tilde{\v\rho}} g_{\tilde{\v\rho}} \v\eta_{\tilde{\v\rho}}
  \1^{\otimes\sum_{\mu,\nu}\tilde\rho^{\mu\nu}_0}
  \bigotimes_{\kappa\ne0}
  \label{eq:Q_K_rho_simp}
where again implicitly
$\sum_\kappa\tilde\rho^{\mu\nu}_\kappa=r_{\mu\nu}$ for consistency
with \eqref{eq:Q_K_eta} and \eqref{eq:Q_K_rho}, and we have explicitly
factored out the identity operators in each term of $Q_{\v K}$.

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from
$\tilde{\v\rho}$) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v\ell,\v r,\v\rho;\v m,\v n,s}}
  f_{\v m\v n\v r\v\rho} P_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the net the prefactor for each term is
\begin{align}
  f_{\v m\v n\v r\v\rho}
  \equiv \sp{\prod_\mu \p{m_\mu}_{\sum_\kappa r_{\mu\kappa}}
    \p{n_\mu}_{\sum_\kappa r_{\kappa\mu}}}
  \sp{\prod_{\mu,\nu,\kappa}
    \f{\p{\eta_{\mu\nu\kappa}}^{\rho^{\mu\nu}_\kappa}}
    {\rho^{\mu\nu}_\kappa!}}
  \sp{N-\sum_\mu\p{m_\mu+n_\mu}+s}
  ^{\sum_{\alpha,\beta}\rho^{\alpha\beta}_0},
\end{align}
and in addition to \eqref{eq:rest_r} the sum over
$\p{\v\ell,\v r,\v\rho;\v m,\v n,s}$ enforces the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \abs{\set{\ell^\mu_a}}
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu.
\end{align}
For clarity, we note here that all indices on
$m_\mu,n_\mu,r_{\mu\nu},\eta_{\mu\nu\kappa},\rho^{\mu\nu}_\kappa$ and
the upper index on $\ell^\mu_a$ take on the same values as the indices
on elements $\sigma_\mu$ of some complete basis for single-spin
operators; of these, only the last index ($\kappa$) on
$\eta_{\mu\nu\kappa},\rho^{\mu\nu}_\kappa$ ever matches the index for
the identity element $\sigma_0\equiv\1$.  The lower index on
$\ell^\mu_a$ indexes the $a$-th spin acted on by a $\sigma_\mu$
operator in each term of \eqref{eq:SS_simp}.
